\section{Introduction}

Belief elicitation in experiments often asks subjects to report probabilities directly.
Frequency reports ask instead for counts: out of \(n\) realizations, how many times will each outcome occur?
This format is natural when the object of interest is a distribution of choices, signals, or outcomes in a finite group.
It may also be easier for subjects than reporting abstract probabilities under a standard scoring rule.\footnote{This cognitive-ease claim is a behavioral premise we inherit from the frequency-format literature \citep{Hogarth1975,GigerenzerHoffrage1995} rather than test ourselves. The claim is that subjects reason more readily in counts than in abstract probabilities and find a distance-based payment more transparent than a probability score---an empirical regularity the literature has documented in adjacent settings but that our exercise does not itself establish. Our informativeness comparison conditions on the report itself: it asks, given that the subject reports under a given count-loss rule, how informative the report is about latent beliefs. Whether the count format also raises the realism of the optimal-reporting assumption is a separate empirical question, taken up in Section~\ref{sec:empirical} as a scope condition on the comparison.}
Many probability scoring rules, including the quadratic scoring rule, are well understood theoretically \citep{Savage1971,GneitingRaftery2007,Selten1998}, but they require subjects to understand how probability reports map into payments.
That mapping can be cognitively demanding, especially when subjects reason more naturally in frequencies than in abstract probabilities \citep{Hogarth1975,GigerenzerHoffrage1995,SchlagEtAl2013}.
Direct monetary scoring rules also raise the familiar risk-aversion problem \citep{ArmantierTreich2012}.

The practical problem is that the researcher observes a count report \(r\), not the subject's latent belief vector \(p\).
The report is an incentivized message generated by a scoring rule.
In other words, the question is inverse: given the rule and the observed report, which beliefs are consistent with optimal reporting?
We follow the chain
\[
S
\;\rightarrow\;
R_S(p)
\;\rightarrow\;
P_S(r)
\;\rightarrow\;
\bigl[\underline p_{S,i}(r),\overline p_{S,i}(r)\bigr].
\]
Here \(S\) is a frequency-report scoring rule, \(R_S(p)\) is the set of reports that are optimal for a subject with beliefs \(p\), and
\[
P_S(r)=\{p\in\Delta^k:r\in R_S(p)\}
\]
is the identified set induced by the observed report.
This recasts incentivized belief elicitation as a partial-identification problem \citep{Manski2003}: the scoring-rule mechanism, rather than a sampling distribution over repeated observations, supplies the identifying restriction.
The final object of the chain is the bound \([\underline p_{S,i}(r),\overline p_{S,i}(r)]\) it yields on each individual probability \(p_i\).
A researcher may also care about functionals of the belief vector, such as a mean or another linear index; bounds on these are obtained from the same identified set \(P_S(r)\).

We use the term \emph{informativeness} in an operational sense.
A rule is more informative for a given design objective if the observed report leads to narrower coordinate bounds or narrower mean and functional bounds.
These inferential gains must be weighed against implementation costs: exact-match payment probabilities, cognitive simplicity, computational burden, and robustness to risk aversion.

Our main analytical contribution is for squared-distance frequency scoring.
Under this rule, a subject reports the feasible count vector closest to the expected count vector \(np\).
This gives a linear identified set and closed-form bounds for each \(p_i\).
Mean bounds and other linear functional bounds are then simple linear programs over the same region.

Extending the partial-identification program of \citet{SchlagTremewan2021}, we compare this rule to two other count-loss mechanisms along a spectrum of analytical tractability.
Frequency-guessing scoring is their known exact-match mechanism: it elicits multinomial modes, gives closed-form bounds, and is robust to risk aversion under a fixed-prize implementation.
Manhattan-distance scoring has an exact identified set and sharp, semi-analytical coordinate bounds.

The contribution is not a new exact-match mechanism and not a general theory of scoring rules; Schlag and Tremewan already derive belief bounds for the frequency-guessing rule.
It is, first, the characterizations themselves: a closed-form identified set and coordinate bounds for squared-distance scoring, the centerpiece result, and sharp semi-analytical bounds for Manhattan distance, alongside the known frequency-guessing bounds.
These three characterizations are not separate facts: a single structural observation---that an optimal report solves a separable resource-allocation problem---organizes them, and a classical convexity criterion then says which rules admit closed-form bounds and which only semi-analytical ones.
It is, second, the contingent decision rule those characterizations make rigorous.
No rule is uniformly best: squared-distance scoring is most informative when the subject's beliefs are concentrated on a few categories and frequency-guessing scoring when beliefs are balanced, with a crossover as concentration varies---first established analytically, where the two closed-form rules' average coordinate widths cross, then quantified and extended to Manhattan distance by the design comparison.
Manhattan is rarely the most informative rule, but its bounds vary little with the regime, making it the robust choice when belief concentration cannot be anticipated.
Partial identification is the lens that holds these together---each scoring rule maps an observed report to an identified set of latent beliefs---and is what lets the comparison be posed as a sharp, finite-sample question rather than an informal one.
Two further count-loss rules, Hamming and Chebyshev distance, mark the boundary of the approach; Section~\ref{sec:other-rules} discusses them as rules whose identified sets are exact but resist tractable sharp bounds.

\paragraph{Related literature.}
Our paper relates to four literatures.

The closest is the work on \emph{frequency guessing}.
The frequency-guessing rule studied here is due to \citet{SchlagTremewan2021}: the subject reports a count vector and wins a fixed prize if it matches the realized counts.
Schlag and Tremewan already establish, for this rule, the three steps we rely on---the optimal report is a multinomial mode, the beliefs consistent with a report form a region of the simplex, and that region yields bounds on individual probabilities and on means and variances through linear programs.
That inferential program, for this one rule, is theirs; the frequency-guessing results in Section~3 restate it so the comparison is self-contained.
The contribution here is to carry the program beyond the rule for which it is known---to squared-distance scoring, where it delivers a closed-form identified set and closed-form coordinate bounds, and to Manhattan distance---and to turn the collection of rules into a comparison.\footnote{The extension is not a routine generalization. Schlag and Tremewan's derivations for the frequency-guessing rule turn on the multinomial-mode structure: a single-count transfer changes the multinomial probability by a closed-form ratio, and the optimality inequalities are linear in \(p\). For a general count loss, neither step survives---the expected loss is not a product, and single-count transfers can fail to be sufficient for optimality even when they are necessary. What unifies the three rules is a structural observation we identify in Section~3: each rule's expected loss reduces to a separable resource-allocation problem in the report \(r\), and discrete convexity of the per-coordinate cost is exactly the condition under which single-count transfers are both necessary and sufficient for optimality. The same condition determines whether the bounds are closed-form (linear in \(p\)) or only semi-analytical (threshold-determined). Hamming and Chebyshev distance are the rules where one of the two hypotheses fails---the limits of the approach, marked in Section~\ref{sec:other-rules}.}
Schlag and Tremewan also show that, for a binary event, frequency guessing is the most precise rule eliciting a single frequency; the question here is the different one of which rule is sharpest across belief regimes, where no rule wins outright.
The boundary with their contribution is therefore three-fold.
Their binary-event dominance result is uniform within their class of single-frequency-eliciting rules; the present comparison is contingent across multinomial belief regimes and rules, and a uniform winner is shown not to exist.
What the partial-identification framework adds beyond restated bounds is a unified treatment of linear-functional inference across rules: mean and linear-functional bounds on a single polytope of single-transfer inequalities for the closed-form rules, and on a single threshold-indexed box-simplex slice for Manhattan, without per-rule bespoke derivations.
\citet{SchlagEtAl2013} survey belief-elicitation methods broadly; we study a specific within-method comparison---frequency-report rules under count losses---that the survey identifies as understudied.

A second literature is the theory of \emph{elicitability}.
The contrast drawn here between the mean-oriented squared-distance rule and the median-oriented Manhattan rule is an instance of a classical correspondence: squared-error loss elicits the mean and absolute-error loss elicits the median \citep{Gneiting2011}, and, more generally, a functional of a distribution is elicitable exactly when its level sets are convex \citep{LambertPennockShoham2008}.
That correspondence is not our contribution; its use is.
The reports studied here are integer count vectors generated against a multinomial law, and each rule is inverted into an identified set of beliefs rather than evaluated as a point forecast.
The frequency-guessing rule sits at the edge of the correspondence: it elicits the multinomial mode, and the mode is not directly elicitable for general distributions---it has the maximal elicitation complexity of the full distribution \citep{LambertPennockShoham2008} and is not elicitable at all in the continuous case \citep{Heinrich2014}.
What makes mode elicitation possible here is the discreteness of the count outcome space, which renders the relevant identified set a polytope.

A third literature concerns what a coarse belief report identifies.
A point forecast does not reveal whether it reports the mean, median, or mode of the underlying distribution \citep{Gneiting2011,EngelbergManskiWilliams2009}, and \citet{EngelbergManskiWilliams2009} accordingly bound the means, medians, and modes of forecasters' subjective distributions from their coarse interval-probability reports.
Set-valued inference about a belief distribution from a coarse report is, in that sense, not new; the difference here is the identifying restriction.
Engelberg, Manski, and Williams take the reported interval probabilities at face value, whereas the identified set \(P_S(r)\) is cut out by the scoring rule's optimality condition---the report is informative only because it was incentive-generated.
The count format itself is also established: survey research elicits subjective probability distributions directly \citep{Manski2004}, often by having respondents allocate a fixed number of tokens or beans across bins \citep{DelavandeGineMcKenzie2011}, which is a frequency report in all but name.

A fourth literature is the experimental study of elicitation methods, surveyed in \citet{SchlagEtAl2013}, \citet{SchotterTrevino2014}, and \citet{CharnessGneezyRasocha2021}.
Two of its recurring concerns are robustness to risk attitudes---direct monetary scoring rules distort reports for risk-averse subjects in ways that depend on stakes and hedging opportunities \citep{ArmantierTreich2012}---and behavioral simplicity.
\citet{TrautmannVanDeKuilen2015} run a ``horse race'' among elicitation mechanisms on the accuracy of the beliefs they recover, and \citet{Offerman2009} keep a standard scoring rule but correct the elicited report ex post for risk attitudes and probability weighting; both aim to recover a point belief, by mechanism choice or by calibration.
The exercise here differs in object: it holds optimal reporting fixed and compares count-loss rules by the sharpness of the belief \emph{set} each report identifies, with no calibration step.
That comparison is conditional on optimal reporting, an assumption that can fail behaviorally---\citet{DanzVesterlundWilson2022} find that the binarized scoring rule, a leading risk-robust mechanism, produces systematically center-biased reports.
The informativeness ranking obtained here is thus an upper bound on what a rule delivers, not a behavioral prediction; Section~\ref{sec:empirical} returns to this as a scope condition.
