\section{Frequency-Report Scoring Rules}

This section characterizes the three headline rules---squared-distance, frequency-guessing, and Manhattan-distance scoring---and then locates the boundary of the approach.
The rules differ in inferential orientation---squared-distance scoring is mean-oriented, frequency-guessing elicits multinomial modes, and Manhattan distance is median-oriented---and they span a spectrum of analytical tractability.
The two rules with closed-form identified sets and closed-form coordinate bounds come first, followed by an analytical comparison of their bounds.
A structural subsection then explains why the two characterizations take the same form---each optimal report solves a separable resource-allocation problem---and supplies the tool that carries the analysis to Manhattan-distance scoring, whose bounds are sharp but semi-analytical: exact, yet located by a one-dimensional numerical step rather than a formula.
The closing subsection characterizes Hamming and Chebyshev distance, the two rules whose count losses fail the structural requirements and which mark where tractable sharp bounds stop.

\subsection{Squared-Distance Scoring: Mean Projection and Closed-Form Bounds}

The analytical centerpiece is squared-distance frequency scoring.
It pays less when the reported count vector is far from the realized count vector in squared Euclidean distance:
\[
S_Q(r,\omega)=a-b\|r-\omega\|_2^2,
\quad b>0.
\]
This rule is connected in spirit to quadratic scoring rules, but it is not a standard probability score.
It is a frequency-report count-loss rule: subjects report counts, and the penalty is the squared difference between reported and realized counts.
Write \(R_Q\) and \(P_Q\) for the report correspondence and identified set induced by this rule.

Given beliefs \(p\), the expected count vector is \(np\).
The key forward fact is that squared-distance scoring asks the subject to report the feasible integer count vector closest to \(np\).
The inverse question is therefore geometric: for which beliefs is the observed report \(r\) the closest feasible count vector to \(np\)?

\begin{proposition}[Squared distance: reports, regions, and bounds]\label{prop:quadratic}
For every \(p\in\DeltaK\),
\[
R_Q(p)
=
\argmin_{s\in\OmegaN}\|s-np\|_2^2.
\]
For an observed report \(r\in\OmegaN\), the identified set is
\[
P_Q(r)
=
\left\{
p\in\DeltaK:
n(p_i-p_j)\le r_i-r_j+1
\quad
\forall i,j\text{ with }r_j>0
\right\}.
\]
Let
\[
m(r)=|\{j:r_j>0\}|
\]
be the number of categories with positive reported counts.
The sharp coordinate intervals are
\[
P_{Q,i}(r)=
\begin{cases}
\displaystyle
\left[0,\frac{m(r)}{n(m(r)+1)}\right],
& r_i=0,\\[1.2em]
\displaystyle
\left[
\frac{r_i-1}{n}+\frac{1}{nk},
\frac{r_i+1}{n}-\frac{1}{n\,m(r)}
\right],
& r_i>0.
\end{cases}
\]
Projection ties are included.
\end{proposition}

The inequalities compare the observed report \(r\) with reports obtained by moving one count from a positive reported category \(j\) to another category \(i\).
If all such single-count moves weakly increase squared distance from \(np\), then \(r\) is a closest feasible report.
Thus \(P_Q(r)\) is a polytope in the belief simplex---a region cut out by finitely many linear inequalities---so sharp bounds on means and other linear functionals \(\sum_i p_ix_i\) are linear programs over the same region that yields the closed-form coordinate intervals.
The proof is in Appendix \ref{app:squared-proof}.

\paragraph{Practical interpretation.}
Squared distance is mean-oriented: it links a report \(r\) to beliefs for which \(r\) is the integer projection of \(np\)---the count-report counterpart of squared-error loss eliciting the mean \citep{Gneiting2011}.
Its main implementation cost is that direct monetary squared-distance payments generally require risk neutrality; the binary-lottery implementation discussed below removes the requirement.

\subsection{Frequency-Guessing Scoring: Multinomial Modes and Closed-Form Bounds}

The second closed-form rule is the frequency-guessing mechanism of \citet{SchlagTremewan2021}.
Its count-error index is the count-vector discrete metric,
\[
D_0(r,\omega)=\1\{r\ne\omega\},
\]
so, in the form \(S_D=a-bD\) of Section~2, the score is
\[
S_0(r,\omega)=a-b\,\1\{r\ne\omega\},
\quad b>0.
\]
Equivalently, \(S_0(r,\omega)=(a-b)+b\,\1\{r=\omega\}\): the subject receives an extra \(b\) whenever the realized count vector equals the report.
This fixed-prize reading is useful for implementation and risk aversion; the two formulations induce the same optimal reports.
Write \(R_0\) and \(P_0\) for the report correspondence and identified set induced by this rule.

The mechanism is simple: a subject with beliefs \(p\) maximizes the probability of an exact match,
\[
\Pr_p(\omega=r)
=
\frac{n!}{r_1!\cdots r_k!}\prod_{i=1}^k p_i^{r_i}.
\]
It follows that the forward object is the multinomial mode set.
The inverse object is the set of beliefs for which the observed report is one of those modes.

\begin{proposition}[Frequency guessing: reports, regions, and bounds]\label{prop:discrete}
Let \(r\in\OmegaN\), and allow ties in the multinomial mode.
Then \(r\) is optimal under frequency-guessing scoring if and only if \(r\) is a multinomial mode:
\[
R_0(p)
=
\argmax_{s\in\OmegaN}\Pr_p(\omega=s).
\]
The identified set is
\[
P_0(r)
=
\left\{
p\in\DeltaK:
r_jp_i\le (r_i+1)p_j
\quad
\forall i,j\text{ with }r_j>0
\right\}.
\]
For each coordinate, the sharp identification interval is
\[
P_{0,i}(r)
=
\left[
\frac{r_i}{n+k-1},
\frac{r_i+1}{n+1}
\right].
\]
\end{proposition}

The inequalities say that no single-count transfer from a reported category \(j\) to another category \(i\) can increase the multinomial probability of the report.
Weak inequalities include ties.
The formula also handles boundaries: if \(r_i=0\), the lower bound is \(0\); if \(r_i=n\), the upper bound is \(1\).
These are the frequency-guessing bounds in \citet[Proposition~1]{SchlagTremewan2021}; they are restated here to make the informativeness comparison self-contained.
\(P_0(r)\) is likewise a polytope, so sharp mean and linear-functional bounds are again linear programs over the joint region rather than combinations of the coordinate intervals.
The proof is in Appendix \ref{app:exact-match-proof}.

\paragraph{Practical interpretation.}
Frequency-guessing scoring is robust to risk aversion under direct payment because winning is a fixed-prize event, as the discussion of risk aversion below makes precise.
Its implementation cost is that the probability of an exact match can be small when \(n\) is large or the outcome space is rich; the design comparison quantifies this.
It is a prominent known rule in the comparison, not a new mechanism introduced here.

\subsection{Comparing the Two Closed-Form Rules}

The closed-form coordinate bounds of Propositions \ref{prop:quadratic} and \ref{prop:discrete} can be compared directly, before any simulation.
For a rule \(S\) and report \(r\), call the mean of the coordinate widths \(\overline p_{S,i}(r)-\underline p_{S,i}(r)\) over the \(k\) coordinates the \emph{average coordinate width}.

\begin{corollary}[Average coordinate width of the closed-form rules]\label{cor:closed-form-comparison}
Fix \(n\ge2\) and \(k\ge2\), and for a report \(r\) let \(m=m(r)\) be the number of categories with positive reported counts.
\begin{enumerate}
\item The frequency-guessing average coordinate width equals the constant
\[
W_0(n,k)=\frac{(k-1)(2n+k)}{k(n+1)(n+k-1)},
\]
the same for every report \(r\).
\item The squared-distance average coordinate width depends on \(r\) only through \(m\):
\[
W_Q(m;n,k)=\frac{1}{nk}\left[2m-1-\frac{m}{k}+\frac{m(k-m)}{m+1}\right].
\]
\item The two widths cross: \(W_Q(1;n,k)<W_0(n,k)<W_Q(k;n,k)\).
\end{enumerate}
\end{corollary}

The proof---elementary algebra on the two coordinate-bound formulas---is in Appendix \ref{app:comparison-proof}.

Parts (1) and (2) together say something clean: the frequency-guessing average width is a constant, while the squared-distance average width is a function of \(m\) alone, so the comparison between the two closed-form rules is decided entirely by \(m=m(r)\), the number of categories the report touches.
Part (3) shows that comparison is not one-sided---the squared-distance average width falls below the frequency-guessing constant at the most concentrated report and rises above it at \(m=k\)---so which rule gives the narrower average coordinate bound genuinely turns on how concentrated the report is.
The design comparison of the next section ties this report-level contrast to belief concentration, quantifies it, and extends it to Manhattan distance.

\subsection{The Common Structure: Optimal Reports as Resource Allocation}

The characterizations of Propositions~\ref{prop:quadratic} and~\ref{prop:discrete} run in parallel: each identified set is cut out by one linear inequality per single-count transfer.
The parallel is structural.
For each headline rule, an optimal report minimizes a \emph{separable} objective over the feasible count vectors,
\[
R_S(p)=\argmin_{r\in\OmegaN}\sum_{i=1}^k\ell(r_i;p_i),
\]
for a per-coordinate cost \(\ell\).
For squared-distance scoring the expected loss is itself additively separable, and \(\ell\) is the expected per-coordinate loss; the same holds for the Manhattan-distance rule \(S_M(r,\omega)=a-b\sum_i|r_i-\omega_i|\), taken up in the next subsection.
Frequency-guessing scoring is not an additively separable loss---the multinomial probability is a product---but maximizing \(\Pr_p(\omega=r)\) is equivalent to minimizing \(\sum_i\{\log(r_i!)-r_i\log p_i\}\), so it has the same form, with \(\ell(t;p_i)=\log(t!)-t\log p_i\).

This is the integer \emph{separable resource-allocation problem}: distribute \(n\) units across \(k\) categories under separable costs.
Its solution structure is classical \citep{Fox1966,FedergruenGroenevelt1986,IbarakiKatoh1988}.
The intuition for what follows is that, under discrete convexity, no local single-count transfer being profitable rules out any larger transfer too: each successive count moved along a path to a competing report is at least as costly as the first.
In other words, the local no-improvement condition is also the global one.

\begin{lemma}[Single-transfer characterization]\label{lem:transfer}
Suppose an optimal report minimizes a separable objective \(\sum_i\ell(r_i;p_i)\) over \(\OmegaN\), and each \(\ell(\cdot;p_i)\) is \emph{discrete-convex}: its successive differences \(\ell(t+1;p_i)-\ell(t;p_i)\) are nondecreasing in \(t\).
Then \(r\) is optimal if and only if no single-count transfer lowers the objective,
\[
\ell(r_i+1;p_i)-\ell(r_i;p_i)\;\ge\;\ell(r_j;p_j)-\ell(r_j-1;p_j)
\qquad\forall\,i,j\text{ with }r_j>0,
\]
and the identified set \(P_S(r)\) is exactly the set of beliefs satisfying these \(O(k^2)\) inequalities.
\end{lemma}

Necessity of the no-transfer condition is immediate: a transfer produces a feasible competing report.
Sufficiency is a monotone-path exchange argument---any competing report is reached by single-count transfers along which discrete convexity makes each step at least as costly as the corresponding transfer evaluated at \(r\); it is proved in Appendix~\ref{app:lemma-proof}.
That the equivalence holds precisely when the per-coordinate costs are discrete-convex is the classical greedy-optimality characterization for separable resource allocation \citep{Fox1966,FedergruenGroenevelt1986}, with discrete convexity the standard diminishing-differences condition \citep{Murota2003}.

The three headline rules satisfy the hypothesis: the squared-distance cost is quadratic in \(r_i\), the Manhattan cost \(\E_p|r_i-\omega_i|\) inherits discrete convexity from the absolute value, and the frequency-guessing cost \(\log(r_i!)-r_i\log p_i\) is discrete-convex because \(\log(t!)\) has nondecreasing differences.
At boundary beliefs the frequency-guessing cost is read in the extended reals---it equals \(+\infty\) when \(p_i=0\) and \(r_i>0\), so optimal reports place no count outside the support of \(p\) (any report concentrated on the support has finite loss); restricted to such reports the lemma applies verbatim, its successive-difference comparisons remaining well defined with the differences extended by continuity from \(p_i\in(0,1)\).

Propositions~\ref{prop:quadratic} and~\ref{prop:discrete} are therefore instances of Lemma~\ref{lem:transfer}, and their single-transfer inequalities are linear in \(p\)---which is why the identified sets are polytopes and the coordinate bounds closed form.
For Manhattan scoring the inequalities are monotone but transcendental in \(p\)---binomial distribution functions rather than linear forms---so no closed form is available; the next subsection shows that the identified set is nonetheless exact and the sharp coordinate bounds reduce to one-dimensional computations.
The lemma thus plays two different roles: for the closed-form rules it organizes what their self-contained proofs already establish, while for Manhattan distance it does real work---sufficiency of the single-transfer condition is exactly what makes the identified set of the next subsection exact rather than an outer approximation.

The lemma's reach is not confined to these three: any count loss of the location form \(\sum_i\psi_i(r_i-\omega_i)\) with convex \(\psi_i\) is governed by it in the same way, because taking expectations preserves discrete convexity coordinate by coordinate---asymmetric-absolute losses, for instance, which elicit quantiles other than the median---so the headline rules are representatives of a wider tractable family rather than a closed list.
The ranked probability score, a squared distance on \emph{cumulative} counts, lies outside this family as stated: its expected loss is separable in the cumulative rather than the per-category counts, and the lemma's transfer argument does not carry over without modification.

The lemma also marks the limits of the approach: its two hypotheses---separability and discrete convexity---are exactly what a count loss can fail, and Section~\ref{sec:other-rules} characterizes the two rules that do.
The optimization content of the lemma is classical; what we add is the observation that incentivized frequency-report elicitation \emph{is} a resource-allocation problem of this kind, and the inversion of the resulting optimal-report correspondence into an identified set of latent beliefs.

\subsection{Manhattan-Distance Scoring: Binomial Medians and Semi-Analytical Bounds}

Unlike the two closed-form rules, Manhattan-distance scoring has no closed-form coordinate bounds; its optimal-report correspondence and identified set are nonetheless characterized exactly, and its sharp bounds reduce to a one-dimensional computation.
The Manhattan-distance rule is
\[
S_M(r,\omega)=a-b\sum_{i=1}^k |r_i-\omega_i|,
\quad b>0.
\]
It rewards total absolute count accuracy rather than squared count accuracy, and its inferential interpretation is median-oriented rather than mean-oriented---the count-report counterpart of absolute-error loss eliciting the median \citep{Gneiting2011}.

For category \(i\) the realized count has binomial marginal \(W_i\sim\mathrm{Bin}(n,p_i)\); write \(F_i(t;n,p_i)=\Pr(W_i\le t)\) for its distribution function, with the conventions \(F_i(-1;n,p_i)=0\) and \(F_i(n;n,p_i)=1\).
By linearity of expectation the expected Manhattan loss is separable across categories, \(\E_p\sum_i|r_i-\omega_i|=\sum_i\E_p|r_i-W_i|\), while the simplex constraint \(\sum_i r_i=n\) couples the coordinates.

\begin{proposition}[Manhattan distance: optimal reports and identified set]\label{prop:manhattan}
Optimal reports minimize the separable expected Manhattan loss,
\[
R_M(p)=\argmin_{r\in\OmegaN}\sum_{i=1}^k\E_p|r_i-W_i|,
\]
and \(r\) is optimal if and only if no single-count transfer lowers that loss, equivalently
\[
F_i(r_i;n,p_i)\ge F_j(r_j-1;n,p_j)
\qquad\forall\,i,j\text{ with }r_i<n,\ r_j>0.
\]
This condition is sufficient as well as necessary, so the identified set is exactly
\[
P_M(r)=\left\{p\in\DeltaK:\ F_i(r_i;n,p_i)\ge F_j(r_j-1;n,p_j)\ \ \forall\,i,j\text{ with }r_i<n,\ r_j>0\right\}.
\]
Equivalently, \(p\in P_M(r)\) if and only if some threshold \(c\in[0,1]\) satisfies
\[
F_i(r_i-1;n,p_i)\le c\le F_i(r_i;n,p_i)\qquad\forall\,i.
\]
\end{proposition}

Each coordinate loss \(\E_p|t-W_i|\) is discrete-convex in the reported count \(t\)---its successive increments are nondecreasing---so Lemma~\ref{lem:transfer} applies and \(P_M(r)\) is the exact identified set rather than an outer approximation.
Weak inequalities include ties, and there is no receiver constraint when \(r_i=n\) nor sender constraint when \(r_j=0\).
The proof is in Appendix~\ref{app:manhattan-proof}.

\paragraph{Identification bounds.}
For \(k=2\), write \(r=(t,n-t)\); the Manhattan loss is \(2|t-W|\) with \(W\sim\mathrm{Bin}(n,p_1)\), and the report identifies the binomial-median interval
\[
P_{M,1}(r)=\{p_1\in[0,1]:F(t-1;n,p_1)\le 1/2\le F(t;n,p_1)\}.
\]
This binary case is clean: for \(n=10\) and the report \(r=(6,4)\), inverting the binomial CDF at \(1/2\) at the integer boundaries \(t-1=5\) and \(t=6\) gives \(P_{M,1}(r)\approx[0.55, 0.64]\)---the set of beliefs at which 6 is a median of \(\mathrm{Bin}(10,p_1)\).

For \(k>2\) the threshold representation of Proposition~\ref{prop:manhattan} drives the bounds.
At a fixed threshold \(c\) the inequalities \(F_i(r_i-1;n,p_i)\le c\le F_i(r_i;n,p_i)\) invert, coordinate by coordinate, to a box of beliefs through inverse binomial CDFs; intersecting that box with the simplex gives the feasible beliefs at that threshold.
Each sharp coordinate bound is then the optimum, over \(c\in[0,1]\), of a function that is unimodal in \(c\), so it is the solution of a single monotone scalar equation; see Lemma~\ref{lem:manhattan-unimodal} in Appendix~\ref{app:manhattan-proof}.
The coordinate bounds are therefore sharp and semi-analytical: not closed form, because the inverse binomial CDF is not elementary, but exact and one-dimensional rather than grid-limited---each coordinate bound is the unique root of the monotone scalar equation of Lemma~\ref{lem:manhattan-unimodal} and is located by bisection.
The sharp \emph{mean} bounds traverse the same threshold parameterization: the identified mean is a linear functional of \(p\) optimized over the same threshold-indexed box-simplex slice, computed on a fine grid of \(c\)-values (with reported tolerance) rather than by a one-dimensional root-find.

\paragraph{Practical interpretation.}
Manhattan distance is median-oriented, as the binomial-median interval above makes concrete.
Its multi-category coordinate bounds are sharp and reduce to a one-dimensional root-find, and its mean bounds are computed on the threshold parameterization to a stated tolerance---exact or tolerance-controlled, not approximations, though not closed form.
The design comparison of the next section gives the rule its practical role: rarely the most informative, but nearly invariant to the belief regime.

\paragraph{Other functionals of the induced outcome distribution.}
The identified sets of all three rules yield bounds on a broader inferential menu---variance, median, other quantiles---when a numerical or ordinal outcome vector is specified. The available functionals depend on what the outcome vector represents (no \(x\): coordinate bounds only; ordinal \(x\): median and quantiles; numerical \(x\): mean, variance, and higher moments). For squared-distance and frequency-guessing the polytope identified sets reduce each functional to a linear program (mean, quantile), a convex quadratic program (variance upper bound), or a vertex search (variance lower bound). For Manhattan-distance the threshold-indexed slice family supports the same operations on each slice; the supremum or infimum is then taken over the threshold parameter, as established in Lemma~\ref{lem:l1-linear} of Appendix~\ref{app:functional-menu}, which also reports a worked example. \citet{SchlagTremewan2021} derive the corresponding bounds for frequency-guessing in their setting; the appendix carries that program to all three rules.

\subsection{Two Rules Outside the Structure: Hamming and Chebyshev Distance}\label{sec:other-rules}

The three rules characterized above do not exhaust the family of count losses, and the partial-identification approach is not a general theory of discrete scoring rules.
Two further rules---Hamming and Chebyshev distance---are worth stating precisely, because they mark where the approach stops yielding tractable sharp bounds.
They are, in fact, the two ways the hypotheses of Lemma~\ref{lem:transfer} can fail: Hamming distance meets its separability hypothesis but not its discrete-convexity hypothesis, and Chebyshev distance fails separability itself.

\paragraph{Hamming distance.}
The Hamming rule \(S_H(r,\omega)=a-b\sum_i\1\{r_i\ne\omega_i\}\) penalizes the number of categories whose reported count differs from the realized count.
By linearity of expectation its expected loss is \(\sum_i\{1-\Pr(\mathrm{Bin}(n,p_i)=r_i)\}\), so an optimal report maximizes the separable objective \(\sum_i\Pr(\mathrm{Bin}(n,p_i)=r_i)\) subject to \(\sum_i r_i=n\), and \(P_H(r)\) is the set of beliefs at which \(r\) attains that maximum---cut out by one expected-loss inequality per alternative report.
For \(k=2\) the two coordinate indicators \(\1\{r_i\ne\omega_i\}\) are equal, so the Hamming count-error index \(\sum_i\1\{r_i\ne\omega_i\}\) is exactly twice the discrete metric \(\1\{r\ne\omega\}\); the rule coincides with frequency-guessing scoring and inherits its closed-form bounds.
For \(k>2\) it does not.
Each term \(\Pr(\mathrm{Bin}(n,p_i)=r_i)\) is unimodal but not discrete-concave in the reported count, so the exchange argument that makes single-count-transfer optimality sufficient for Manhattan distance fails here: the condition remains necessary but is no longer sufficient, because a transfer of two or more counts can raise the separable objective where no single-count transfer does.
This failure is not confined to the boundary of the simplex.
At \(n=3\), \(k=5\), and uniform beliefs \(p=(1/5,\ldots,1/5)\), for instance, the report \((3,0,0,0,0)\) admits no improving single-count transfer, yet \((0,0,1,1,1)\) yields a strictly higher expected score.
The instance also certifies that the failure is not an artifact of the particular separable representation: a strictly increasing transformation of the expected \emph{loss} preserves both rankings---\((3,0,0,0,0)\) attains weakly lower transformed loss than each of its single-transfer neighbours while \((0,0,1,1,1)\) attains strictly lower transformed loss---so if any such transformation admitted a separable representation with discrete-convex per-coordinate costs, Lemma~\ref{lem:transfer} would force \((3,0,0,0,0)\) to be globally optimal at these beliefs; none therefore exists.
The logarithmic transformation that separates the frequency-guessing score has no Hamming counterpart.
The identified set \(P_H(r)\) is therefore a non-convex set defined by polynomial inequalities, not a polytope.
The modal box \(\prod_i[r_i/(n+1),(r_i+1)/(n+1)]\) collects the beliefs at which every \(r_i\) is a mode of its binomial marginal; there the separable objective is maximized term by term, so \(r\) is optimal, and the modal box is a closed-form inner bound for \(P_H(r)\), while the single-count-transfer inequalities give an outer bound.
The sharp coordinate bounds lie between these two and require optimizing a coordinate directly over the non-convex set---a global optimization whose feasible region is cut out by one polynomial inequality for each of the \(\binom{n+k-1}{k-1}\) feasible reports, a constraint count that grows combinatorially and exceeds \(10^{10}\) at the largest cell of the design comparison of Section~\ref{sec:design} (\(n=50\), \(k=10\)).
A direct feasibility check bore out the obstruction: computing the sharp Hamming bounds proved both prohibitively slow and numerically unreliable for \(k=10\), while the closed-form bounds of the other rules are immediate.
Hamming distance is for this reason characterized here rather than included in the comparison.

\paragraph{Chebyshev distance.}
The Chebyshev rule \(S_\infty(r,\omega)=a-b\max_i|r_i-\omega_i|\) penalizes the largest single-category count error.
Unlike the other count losses, its expected loss does not separate across coordinates: the maximum couples the category errors within every realization, so there is no per-coordinate transfer condition to exploit.
For \(k=2\) the two absolute errors \(|r_i-\omega_i|\) are equal, so the count-error index \(\max_i|r_i-\omega_i|\) is half of \(\sum_i|r_i-\omega_i|\); the rule coincides with Manhattan scoring and inherits the binomial-median interval.
For \(k>2\) neither half of the pipeline is tractable at scale.
The non-separable objective admits no transfer or exchange argument, so no characterization of the optimal report beyond search is known: a certified optimal report must be found by comparing all \(\binom{n+k-1}{k-1}\) feasible reports.
The identified set, in turn, is cut out only by the full system of expected-loss inequalities, one per alternative report, with no transfer-polytope or threshold reduction---the same kind of non-convex semialgebraic set as \(P_H(r)\), whose sharp bounds the Hamming feasibility check above already found intractable at \(k=10\).
Chebyshev distance is therefore computable by enumeration for small \(n\) and \(k\) but, like Hamming, cannot be carried across the design grid; it is characterized here rather than included in the comparison.

These two rules are not pathological---their identified sets are well defined and finite to check---but they show that the closed-form and semi-analytical tractability of the headline rules is a property of those rules, not a generic feature of count-loss scoring.
