\appendix

\section{Proofs}

\subsection{Squared-Distance Scoring}
\label{app:squared-proof}

\begin{proof}[Proof of Proposition~\ref{prop:quadratic}]
Maximizing \(S_Q\) is equivalent to minimizing \(\E_p\|r-\omega\|_2^2\).
For fixed \(r\),
\[
\E_p\|r-\omega\|_2^2
=
\|r-\E_p[\omega]\|_2^2
+
\sum_{i=1}^k\mathrm{Var}_p(\omega_i).
\]
The variance term is independent of \(r\), and \(\E_p[\omega]=np\).
Hence optimal reports are exactly the feasible integer projections of \(np\).

The full inverse projection condition is
\[
\|r-np\|_2^2\le \|s-np\|_2^2
\quad
\forall s\in\OmegaN,
\]
or equivalently
\[
2np\cdot(s-r)\le \|s\|_2^2-\|r\|_2^2.
\]
Taking \(s=r+e_i-e_j\), feasible when \(r_j>0\), gives
\[
n(p_i-p_j)\le r_i-r_j+1.
\]
Conversely, suppose all these single-count inequalities hold.
For any \(s\in\OmegaN\), write \(d=s-r\).
Pair each positive unit of \(d_i\) with a negative unit of \(d_j\).
Each coordinate \(j\) with \(d_j<0\) has \(s_j<r_j\) and hence \(r_j>0\), so the single-count inequality \(n(p_i-p_j)\le r_i-r_j+1\) is available for every paired transfer.
Summing the single-count inequalities over the paired transfers gives
\[
np\cdot d\le r\cdot d+M,
\]
where \(M=\sum_{i:d_i>0}d_i\) is the number of transferred counts.
Because \(d\) has integer components, \(|d_i|\ge 1\) on its support, so
\[
\sum_i d_i^2\ge\sum_i |d_i|=2M.
\]
Doubling the displayed inequality and substituting \(2M\le\sum_i d_i^2=\|d\|_2^2\) gives \(2np\cdot d\le 2r\cdot d+\|d\|_2^2\).
Since \(d=s-r\),
\[
2np\cdot(s-r)
\le
2r\cdot(s-r)+\|s-r\|_2^2
=
\|s\|_2^2-\|r\|_2^2,
\]
which is the full projection condition.

It remains to derive the coordinate bounds.
Let \(m=m(r)=|\{j:r_j>0\}|\).
If \(r_i>0\), summing
\[
n(p_u-p_i)\le r_u-r_i+1
\]
over all \(u\ne i\) gives
\[
1-p_i\le (k-1)p_i+\frac{n-kr_i+k-1}{n},
\]
so
\[
p_i\ge \frac{r_i-1}{n}+\frac{1}{nk}.
\]
For the upper bound, sum
\[
n(p_i-p_v)\le r_i-r_v+1
\]
over the \(m-1\) positive-report coordinates \(v\ne i\); since the remaining coordinates have \(r_v=0\) and therefore contribute \(p_v\ge 0\) to the simplex sum, \(\sum_{v\ne i, r_v>0}p_v\le 1-p_i\), which gives
\[
1-p_i\ge (m-1)p_i+\frac{n-mr_i-m+1}{n}.
\]
This gives
\[
p_i\le \frac{r_i+1}{n}-\frac{1}{nm}.
\]

If \(r_i=0\), the lower bound is \(0\).
For the upper bound, sum
\[
n(p_i-p_v)\le 1-r_v
\]
over all \(m\) positive-report coordinates \(v\):
\[
1-p_i\ge mp_i+\frac{n-m}{n},
\]
so
\[
p_i\le \frac{m}{n(m+1)}.
\]
The bounds are sharp, with an explicit attaining belief for each endpoint.
For the lower bound with \(r_i>0\), take \(p_i=(r_i-1)/n+1/(nk)\) and \(p_u=r_u/n+1/(nk)\) for \(u\ne i\).
This is a probability vector---it sums to one and every coordinate is at least \(1/(nk)\)---and \(n(p_a-p_b)=r_a-r_b\le r_a-r_b+1\) for \(a,b\ne i\) while \(n(p_a-p_i)=r_a-r_i+1\), so it lies in \(P_Q(r)\) and the constraints with \(b=i\) bind, attaining the lower endpoint.
For the upper bound with \(r_i>0\), take \(p_i=(r_i+1)/n-1/(nm)\), take \(p_v=r_v/n-1/(nm)\) for the positive-report coordinates \(v\ne i\), and set \(p_v=0\) for the zero-report coordinates.
This sums to one and is nonnegative, lies in \(P_Q(r)\), and makes the constraints \(n(p_i-p_v)\le r_i-r_v+1\) bind for every positive-report \(v\ne i\), attaining the upper endpoint.
For the upper bound with \(r_i=0\), take \(p_i=m/(n(m+1))\), take \(p_v=\{(m+1)r_v-1\}/(n(m+1))\) for the positive-report coordinates \(v\), and set \(p_w=0\) for the other zero-report coordinates.
This sums to one and is nonnegative, lies in \(P_Q(r)\), and makes the constraints \(n(p_i-p_v)\le 1-r_v\) bind, attaining the upper endpoint.
Thus the displayed bounds are sharp.
\end{proof}

\subsection{Frequency-Guessing Scoring}
\label{app:exact-match-proof}

\begin{proof}[Proof of Proposition~\ref{prop:discrete}]
For any report \(r\),
\[
\E_p[S_0(r,\omega)]
=
a-b\Pr_p(\omega\ne r)
=
(a-b)+b\Pr_p(\omega=r),
\]
so, since \(b>0\), expected-score maximization is equivalent to maximizing the multinomial probability mass \(\Pr_p(\omega=r)\).

It remains to characterize the mode region.
Compare \(r\) with \(r+e_i-e_j\), which is feasible when \(r_j>0\).
If \(p_j=0\) and \(r_j>0\), then \(r\) cannot be a mode unless all probability is zero, which is impossible.
For \(p_j>0\),
\[
\frac{\Pr_p(r+e_i-e_j)}{\Pr_p(r)}
=
\frac{r_j}{r_i+1}\frac{p_i}{p_j}.
\]
Thus a necessary condition for \(r\) to be a mode is
\[
r_jp_i\le (r_i+1)p_j
\quad
\forall i,j\text{ with }r_j>0.
\]
Conversely, if these inequalities hold, any feasible \(s\) can be reached from \(r\) by a sequence of single-count transfers from coordinates where the current vector exceeds \(s\) to coordinates where it is below \(s\).
At each step the same ratio is at most one, because source counts weakly decrease and destination counts weakly increase along the path.
Therefore no feasible \(s\) has larger multinomial mass than \(r\).

The coordinate upper bound follows by summing
\[
r_jp_i\le (r_i+1)p_j
\]
over \(j\ne i\):
\[
(n-r_i)p_i\le (r_i+1)(1-p_i),
\]
so \(p_i\le (r_i+1)/(n+1)\).
The lower bound follows by summing
\[
r_ip_j\le (r_j+1)p_i
\]
over \(j\ne i\):
\[
r_i(1-p_i)\le (n-r_i+k-1)p_i,
\]
so \(p_i\ge r_i/(n+k-1)\).

The bounds are sharp.
The upper endpoint is attained by
\[
p_i=\frac{r_i+1}{n+1},
\quad
p_j=\frac{r_j}{n+1}\quad(j\ne i).
\]
The lower endpoint, when \(r_i>0\), is attained by
\[
p_i=\frac{r_i}{n+k-1},
\quad
p_j=\frac{r_j+1}{n+k-1}\quad(j\ne i).
\]
When \(r_i=0\), the lower endpoint \(0\) is attained by setting \(p_i=0\) and assigning probabilities proportional to \(r_j\) on the reported support.
When \(r_i=n\), the upper endpoint \(1\) is attained by \(p_i=1\).
\end{proof}

\subsection{Comparing the Two Closed-Form Rules}
\label{app:comparison-proof}

\begin{proof}[Proof of Corollary \ref{cor:closed-form-comparison}]
Throughout, \(m=m(r)\) is the number of categories with \(r_i>0\), and the average coordinate width is \((1/k)\sum_{i=1}^k(\overline p_i-\underline p_i)\).

\emph{Part (1).} By Proposition \ref{prop:discrete} the frequency-guessing coordinate width is
\[
\frac{r_i+1}{n+1}-\frac{r_i}{n+k-1}
=\frac{r_i(k-2)+(n+k-1)}{(n+1)(n+k-1)}.
\]
Summing over \(i\) and using \(\sum_i r_i=n\),
\[
\sum_{i=1}^k\left(\overline p_{0,i}-\underline p_{0,i}\right)
=\frac{(k-2)n+k(n+k-1)}{(n+1)(n+k-1)}
=\frac{(k-1)(2n+k)}{(n+1)(n+k-1)};
\]
dividing by \(k\) gives \(W_0(n,k)\), which does not depend on \(r\).

\emph{Part (2).} By Proposition \ref{prop:quadratic} a positive-report category has coordinate width \(2/n-1/(nm)-1/(nk)\) and a zero-report category has width \(m/[n(m+1)]\). With \(m\) positive and \(k-m\) zero categories,
\[
\sum_{i=1}^k\left(\overline p_{Q,i}-\underline p_{Q,i}\right)
=m\left(\frac{2}{n}-\frac{1}{nm}-\frac{1}{nk}\right)+(k-m)\frac{m}{n(m+1)}
=\frac{1}{n}\left[2m-1-\frac{m}{k}+\frac{m(k-m)}{m+1}\right];
\]
dividing by \(k\) gives \(W_Q(m;n,k)\), a function of \(m\) alone.

\emph{Part (3).} Evaluating part (2) at \(m=k\) gives \(W_Q(k;n,k)=2(k-1)/(nk)\), and
\[
W_Q(k;n,k)>W_0(n,k)
\iff 2(n+1)(n+k-1)>n(2n+k)
\iff k(n+2)>2,
\]
which holds for all \(n\ge1\) and \(k\ge2\). Evaluating at \(m=1\) gives \(W_Q(1;n,k)=(k-1)(k+2)/(2nk^2)\), and
\[
W_Q(1;n,k)<W_0(n,k)
\iff (k+2)(n+1)(n+k-1)<2nk(2n+k).
\]
The right side minus the left equals \(n^2(3k-2)+nk(k-2)-(k+2)(k-1)\), whose coefficients in \(n\) are nonnegative for \(k\ge2\), so it is increasing in \(n\); at \(n=2\) it equals \(k^2+7k-6>0\). Hence \(W_Q(1;n,k)<W_0(n,k)\) for all \(n\ge2\) and \(k\ge2\).
\end{proof}

\subsection{The Single-Transfer Characterization}
\label{app:lemma-proof}

\begin{proof}[Proof of Lemma~\ref{lem:transfer}]
Write \(\Delta\ell(t;q)=\ell(t+1;q)-\ell(t;q)\); discrete convexity of \(\ell(\cdot;q)\) means \(\Delta\ell(\cdot;q)\) is nondecreasing.

\emph{Necessity.}
For any \(i,j\) with \(r_j>0\) the report \(r+e_i-e_j\) is feasible, and it changes the objective by \(\Delta\ell(r_i;p_i)-\Delta\ell(r_j-1;p_j)\).
If \(r\) is optimal this change is nonnegative, which is the displayed inequality.

\emph{Sufficiency.}
Suppose \(r\) satisfies every displayed inequality, and let \(s\in\OmegaN\) be any competing report.
Since \(\sum_i s_i=\sum_i r_i=n\), the surplus units \(\sum_i(s_i-r_i)^+\) and the deficit units \(\sum_j(r_j-s_j)^+\) are equal in number, say \(M\).
Reach \(s\) from \(r\) by \(M\) single-count transfers, each moving one unit from a coordinate still above its target \(s\) to one still below.
A receiver coordinate then only rises, from \(r_i\) toward \(s_i\), and a sender only falls, from \(r_j\) toward \(s_j\); so every intermediate report is feasible, and at the step transferring a unit \(j\to i\) the running counts satisfy \(c_i\ge r_i\) and \(c_j\le r_j\).
That step changes the objective by \(\Delta\ell(c_i;p_i)-\Delta\ell(c_j-1;p_j)\).
Because \(\Delta\ell(\cdot;p)\) is nondecreasing, \(c_i\ge r_i\) gives \(\Delta\ell(c_i;p_i)\ge\Delta\ell(r_i;p_i)\), and \(c_j-1\le r_j-1\) gives \(\Delta\ell(c_j-1;p_j)\le\Delta\ell(r_j-1;p_j)\); so the step's change is at least \(\Delta\ell(r_i;p_i)-\Delta\ell(r_j-1;p_j)\), nonnegative by the displayed inequality for the pair \((i,j)\).
Summing over the \(M\) steps gives \(\sum_i\ell(s_i;p_i)\ge\sum_i\ell(r_i;p_i)\).
As \(s\) was arbitrary, \(r\) minimizes the separable objective.

Necessity and sufficiency together give \(r\in R_S(p)\) if and only if the displayed inequalities hold at \(p\), so \(P_S(r)\) is exactly the set of beliefs satisfying them.
\end{proof}

\subsection{Manhattan-Distance Scoring}
\label{app:manhattan-proof}

\begin{proof}[Proof of Proposition~\ref{prop:manhattan}]
Linearity of expectation gives
\[
\E_p\left[\sum_{i=1}^k |r_i-\omega_i|\right]
=
\sum_{i=1}^k \E_p|r_i-\omega_i|.
\]
The \(i\)-th term depends only on the binomial marginal \(W_i\sim\mathrm{Bin}(n,p_i)\).
For
\[
\ell_i(t;p_i)=\E|t-W_i|,
\]
the marginal cost of increasing the reported count from \(t\) to \(t+1\) is
\[
\ell_i(t+1;p_i)-\ell_i(t;p_i)
=
2F_i(t;n,p_i)-1.
\]
Moving one reported count from \(j\) to \(i\) changes expected Manhattan loss by
\[
\{2F_i(r_i;n,p_i)-1\}-\{2F_j(r_j-1;n,p_j)-1\}.
\]
Hence no feasible single-count transfer improves the report if and only if
\[
F_i(r_i;n,p_i)\ge F_j(r_j-1;n,p_j)
\quad
\forall i,j\text{ with }r_i<n,\ r_j>0.
\]
The increments \(2F_i(t;n,p_i)-1\) are weakly increasing in \(t\), so each coordinate loss \(\ell_i(\cdot;p_i)\) is discrete-convex; Lemma~\ref{lem:transfer} then applies, and the no-transfer condition just derived is sufficient as well as necessary---so \(P_M(r)\) is the exact identified set.

The threshold representation follows by taking \(c\) between
\[
\max_{j:r_j>0}F_j(r_j-1;n,p_j)
\quad\text{and}\quad
\min_{i:r_i<n}F_i(r_i;n,p_i).
\]
Inverting the resulting binomial-CDF inequalities coordinate by coordinate gives the threshold-indexed box-simplex description used for Manhattan bounds.
\end{proof}

For \(t\in\{0,\dots,n-1\}\) the binomial CDF \(F(t;n,p)=\sum_{j=0}^t\binom{n}{j}p^j(1-p)^{n-j}\) is continuous and strictly decreasing in \(p\) on \([0,1]\), with \(F(t;n,0)=1\) and \(F(t;n,1)=0\); together with the conventions \(F(-1;n,p)=0\) and \(F(n;n,p)=1\) this lets us define, for each \(c\in[0,1]\) and each coordinate \(v\), the threshold-indexed endpoints
\begin{align*}
p_v^{(L)}(c)&=
\begin{cases}
\text{the unique }p\in[0,1]\text{ with }F(r_v-1;n,p)=c, & r_v>0,\\
0, & r_v=0,
\end{cases}\\
p_v^{(U)}(c)&=
\begin{cases}
\text{the unique }p\in[0,1]\text{ with }F(r_v;n,p)=c, & r_v<n,\\
1, & r_v=n.
\end{cases}
\end{align*}
Both \(c\mapsto p_v^{(L)}(c)\) and \(c\mapsto p_v^{(U)}(c)\) are continuous and weakly decreasing in \(c\) on \([0,1]\), strictly so on the range where the corresponding case is non-degenerate.

\begin{lemma}[Single-equation characterization of Manhattan coordinate bounds]\label{lem:manhattan-unimodal}
Fix \(r\in\OmegaN\) and a coordinate \(i\).
\begin{enumerate}
\item[(i)] If \(r_i<n\), the sharp upper bound \(\bar p_i(r)=\sup\{p_i:p\in P_M(r)\}\) equals \(p_i^{(U)}(c^*)\), where \(c^*\in[0,1]\) is the unique solution of
\[
p_i^{(U)}(c)+\sum_{v\ne i}p_v^{(L)}(c)=1.
\]
\item[(ii)] If \(r_i>0\), the sharp lower bound \(\underline p_i(r)=\inf\{p_i:p\in P_M(r)\}\) equals \(p_i^{(L)}(c^{**})\), where \(c^{**}\in[0,1]\) is the unique solution of
\[
p_i^{(L)}(c)+\sum_{v\ne i}p_v^{(U)}(c)=1.
\]
\end{enumerate}
Each defining equation is continuous and strictly monotone in \(c\), so each bound is the solution of a single monotone scalar equation and can be located by bisection on \([0,1]\).
\end{lemma}

\begin{proof}
For (i), Proposition~\ref{prop:manhattan} gives \(p\in P_M(r)\) iff there is a threshold \(c\in[0,1]\) with \(p_v^{(L)}(c)\le p_v\le p_v^{(U)}(c)\) for all \(v\). At a fixed \(c\), maximizing \(p_i\) over the box-simplex slice attains \(p_i^{(U)}(c)\) iff the residual mass \(1-p_i^{(U)}(c)\) admits a feasible decomposition over \(v\ne i\), i.e.\ iff
\(\sum_{v\ne i}p_v^{(L)}(c)\le 1-p_i^{(U)}(c)\le\sum_{v\ne i}p_v^{(U)}(c)\); otherwise the maximum is \(1-\sum_{v\ne i}p_v^{(L)}(c)<p_i^{(U)}(c)\). Hence the sliced maximum is
\[
\phi(c):=\min\!\big(p_i^{(U)}(c),\ 1-\textstyle\sum_{v\ne i}p_v^{(L)}(c)\big),
\]
and \(\bar p_i(r)=\sup_{c\in[0,1]}\phi(c)\). The first argument \(p_i^{(U)}(c)\) is continuous and weakly decreasing in \(c\), while the second argument \(1-\sum_{v\ne i}p_v^{(L)}(c)\) is continuous and weakly increasing in \(c\) (since each \(p_v^{(L)}\) is weakly decreasing); their unique crossing is the \(c^*\) where \(p_i^{(U)}(c^*)+\sum_{v\ne i}p_v^{(L)}(c^*)=1\), and \(\phi\) is unimodal in \(c\) with peak at \(c^*\). For \(c<c^*\), \(\phi(c)=1-\sum_{v\ne i}p_v^{(L)}(c)\le 1-\sum_{v\ne i}p_v^{(L)}(c^*)=p_i^{(U)}(c^*)\) (strict decrease of \(\sum_{v\ne i}p_v^{(L)}\)); for \(c>c^*\), \(\phi(c)=p_i^{(U)}(c)\le p_i^{(U)}(c^*)\) (strict decrease of \(p_i^{(U)}\)). So \(\phi\) attains its maximum at \(c^*\) with value \(p_i^{(U)}(c^*)\), and \(c^*\) is the unique solution of the displayed equation since its left-hand side is continuous and strictly decreasing in \(c\) (from a value \(\ge 1\) at \(c=0\) to \(0\) at \(c=1\)). Part (ii) is symmetric, exchanging the roles of \(p_v^{(L)}\) and \(p_v^{(U)}\).
\end{proof}

\subsection{Bounds on Additional Functionals of the Induced Outcome Distribution}\label{app:functional-menu}

The bounds developed in the body have been on individual coordinates of \(p\) and on the linear functional \(\sum_i x_i p_i\) for a numerical outcome vector \(x\). The same identified sets yield bounds on a broader inferential menu---variance, median, other quantiles---with the available functionals depending on what \(x\) represents.

\paragraph{The role of \(x\).} Three regimes cover the cases of practical interest.
\begin{enumerate}
\item[(i)] \emph{No \(x\).} Only coordinate bounds \([\underline p_{S,i}(r), \overline p_{S,i}(r)]\) are meaningful---probabilities of individual unordered categories.
\item[(ii)] \emph{Ordinal \(x\).} Categories carry an ordering \(x_1<x_2<\cdots<x_k\) but the values are nominal; the menu adds bounds on the median \(\mathrm{Med}(Y)\) and other quantiles \(q_\tau(Y)\) of the induced random variable \(Y=x_J\), \(J\sim p\).
\item[(iii)] \emph{Numerical \(x\).} Categories have numerical values in \(\R^k\); the menu adds bounds on the mean \(\E(Y)\), variance \(\mathrm{Var}(Y)\), and any polynomial functional of the induced outcome distribution.
\end{enumerate}

\paragraph{General machinery.} For any functional \(T:\Delta^k\to\R\), the identified bound under rule \(S\) is the pair
\[
\Big[\inf_{p\in P_S(r)} T(p),\ \sup_{p\in P_S(r)} T(p)\Big].
\]
The geometry of \(P_S(r)\) determines which optimization machinery applies. Squared-distance and frequency-guessing scoring induce polytope identified sets, so linear \(T\) (mean) reduces to a linear program; the variance \(\mathrm{Var}(Y)=\sum_i x_i^2 p_i-(\sum_i x_i p_i)^2\) is concave in \(p\), so its upper bound is a convex quadratic program over the polytope and its lower bound is a non-convex minimum attained at a polytope vertex; and a step-function \(T\)---the \(\tau\)-quantile index \(j^*_\tau(p)=\min\{j:S_j(p)\ge\tau\}\) with \(S_j(p)=\sum_{i\le j}p_i\), and any monotone transformation of it including the median---reduces to a sequence of linear programs over the polytope, one per candidate value of \(j^*_\tau\). Manhattan-distance scoring induces a threshold-indexed slice family rather than a polytope (Proposition~\ref{prop:manhattan}), but the same operations apply on each slice and the optimum is then taken over the threshold parameter.

The threshold representation gives a particularly clean characterization for cumulative sums, the building blocks of median and quantile bounds.

\begin{lemma}[Linear functionals over the Manhattan identified set]\label{lem:l1-linear}
Fix \(r\in\OmegaN\). For any vector \(a\in\R^k\),
\[
\sup_{p\in P_M(r)} \sum_i a_i p_i
\;=\;
\sup_{c\in[0,1]}\,\sup\Big\{\textstyle\sum_i a_i p_i \;:\; p_v^{(L)}(c)\le p_v\le p_v^{(U)}(c)\;\forall v,\ \sum_v p_v=1\Big\},
\]
and analogously for the infimum, where \(p_v^{(L)}(c),p_v^{(U)}(c)\) are the threshold-indexed endpoints from Lemma~\ref{lem:manhattan-unimodal} and the inner supremum is taken with the convention \(-\infty\) when the slice is empty. The inner supremum is a linear program over a box-simplex slice. Applied to the indicator vector \(a=(\1\{i\le j\})_{i=1}^k\), this yields the cumulative-sum bounds \(\sup_{p\in P_M(r)} S_j(p)\) and \(\inf_{p\in P_M(r)} S_j(p)\); the \(\tau\)-quantile-index bound on the induced \(Y\) follows from
\[
\min_{p}j^*_\tau(p)=\min\{j:\sup_p S_j(p)\ge\tau\},\qquad \max_{p}j^*_\tau(p)=\max\{j:\inf_p S_{j-1}(p)<\tau\}.
\]
\end{lemma}

\begin{proof}
By Proposition~\ref{prop:manhattan}, \(p\in P_M(r)\) iff there is a threshold \(c\in[0,1]\) with \(p_v^{(L)}(c)\le p_v\le p_v^{(U)}(c)\) for all \(v\). Equivalently, \(P_M(r)=\bigcup_{c\in[0,1]}\Sigma(c)\), where \(\Sigma(c)=\{p\in\Delta^k:p_v^{(L)}(c)\le p_v\le p_v^{(U)}(c)\,\forall v\}\). For any \(a\in\R^k\),
\[
\sup_{p\in P_M(r)} \textstyle\sum_i a_i p_i
\;=\;\sup_{c\in[0,1]}\,\sup_{p\in\Sigma(c)}\textstyle\sum_i a_i p_i,
\]
since the supremum over a union equals the supremum of suprema. The inner problem at fixed \(c\) is a linear program over the box-simplex slice \(\Sigma(c)\); the analogous identity holds for the infimum. Specialising to \(a_i=\1\{i\le j\}\) gives the cumulative-sum bounds \(\sup_{p\in P_M(r)} S_j(p)\) and \(\inf_{p\in P_M(r)} S_j(p)\) for each \(j\).

For the quantile-index bounds, since \(S_j(p)\) is nondecreasing in \(j\), \(j^*_\tau(p)\le j\) iff \(S_j(p)\ge\tau\), and \(j^*_\tau(p)\ge j\) iff \(S_{j-1}(p)<\tau\) (with \(S_0\equiv 0\)). Hence
\[
\min_{p\in P_M(r)}j^*_\tau(p)=\min\{j:\sup_{p\in P_M(r)} S_j(p)\ge\tau\},\quad
\max_{p\in P_M(r)}j^*_\tau(p)=\max\{j:\inf_{p\in P_M(r)} S_{j-1}(p)<\tau\}.
\]
The one-parameter family of box-simplex linear programs is solved by sweeping \(c\) on a fine grid (with the tolerance reported in Appendix~\ref{app:design-details}).
\end{proof}

\paragraph{Worked example.}
Take \(n=10\), \(k=5\), report \(r=(2,2,2,2,2)\), and numerical outcomes \(x=(0,1,2,3,4)\)---the symmetric report at which the no-universal-winner conclusion of Section~\ref{sec:design} is most visible. Table~\ref{tab:functional-menu} reports the bounds.

\begin{table}[h]
\centering
\small
\begin{tabular}{lccc}
\hline
Functional & Frequency-guessing & Squared-distance & Manhattan\\
\hline
Each \(p_i\)                                  & \([0.143,\,0.273]\) & \([0.120,\,0.280]\) & \([0.129,\,0.280]\)\\
Mean \(\E(Y)\)                                & \([1.75,\,2.25]\)   & \([1.70,\,2.30]\)   & \([1.71,\,2.29]\)\\
Median \(\mathrm{Med}(Y)\)                    & \(\{1,2\}\)         & \(\{1,2,3\}\)       & \(\{1,2,3\}\)\\
Lower quartile \(q_{0.25}(Y)\)                & \(\{0,1\}\)         & \(\{0,1\}\)         & \(\{0,1\}\)\\
Upper quartile \(q_{0.75}(Y)\)                & \(\{3,4\}\)         & \(\{3,4\}\)         & \(\{3,4\}\)\\
\hline
\end{tabular}
\caption{Identified bounds for \(n=10\), \(k=5\), \(r=(2,2,2,2,2)\), \(x=(0,1,2,3,4)\). Frequency-guessing gives the tightest mean and median bounds at this symmetric report; the rules coincide on the upper and lower quartiles. Variance bounds follow from a constrained optimization over the same identified sets (a convex quadratic program for the upper bound, a vertex search for the lower) and are omitted to keep the table compact.}
\label{tab:functional-menu}
\end{table}

Two structural observations. First, the inferential menu---coordinate, mean, variance, median, quantile---is unified through the identified set rather than through rule-specific machinery; each functional is the same optimization problem with a different objective. Second, the no-universal-winner conclusion of Section~\ref{sec:design} extends to non-linear functionals: which rule yields the tightest bound depends jointly on the report shape and the chosen functional. The Gneiting (2011) correspondence between absolute-error loss and the median, invoked in the body at the level of optimal reports, is a statement about \emph{elicitation}, not \emph{identified-set tightness}: at the symmetric report displayed in Table~\ref{tab:functional-menu} the median-eliciting Manhattan rule does not give tighter median bounds than frequency-guessing. \citet{SchlagTremewan2021} derive bounds on means, variances, and quantiles for frequency-guessing in their setting; the statement above carries that program across all three rules.

\section{Design Comparison Details}
\label{app:design-details}

The design comparison is generated by the script \texttt{scripts/design\_efficiency.py}.
The final grid uses \(n\in\{5,10,20,50\}\), \(k\in\{2,3,5,10\}\), \(\alpha\in\{0.1,0.3,1,3,10\}\), and \(5{,}000\) draws from the symmetric Dirichlet distribution for each cell.
For each draw, and for each of the three rules in the comparison---frequency-guessing, squared-distance, and Manhattan---the script computes an optimal report and then bounds for the identified set generated by that report.
Hamming and Chebyshev distance are excluded; Section~\ref{sec:other-rules} explains why their identified sets do not yield tractable sharp bounds.

Frequency-guessing coordinate bounds are closed form and mean bounds are linear programs over the transfer region.
Squared-distance coordinate bounds are closed form and mean bounds are linear programs over the single-count transfer polytope.
Manhattan coordinate bounds are sharp: the script solves the one-dimensional threshold optimization implied by Appendix \ref{app:manhattan-proof} with a monotone root-find.
Manhattan mean bounds use the same threshold representation but are computed over a threshold grid with tolerance \(10^{-4}\).

The generated files are CSV tables under \texttt{outputs/design\_exercise/}.
These outputs are diagnostics for experimental design.
They are not simulations of subject behavior and do not replace the mathematical characterization of \(R_S(p)\) and \(P_S(r)\).

Table~\ref{tab:design-nk} substantiates the claim in Section~4 that the number of categories \(k\) and the number of trials \(n\) are second-order.
It reports win shares marginally by \(k\) and by \(n\), averaging over the other two design dimensions.
Against the variation across belief concentration \(\alpha\) in Table~\ref{tab:regime-wins}---where the leading rule's win share runs from near zero to one---the dependence on \(k\) and \(n\) is slight.

\begin{table}[h]
\centering
\small
\begin{tabular}{lrrrrrr}
\hline
& \multicolumn{3}{c}{Average-coordinate} & \multicolumn{3}{c}{Linear-mean}\\
\cline{2-4}\cline{5-7}
& Guessing & Squared & Manhattan & Guessing & Squared & Manhattan\\
\hline
\multicolumn{7}{l}{By number of categories \(k\)}\\
2  & 0.72 & 0.25 & 0.03 & 0.72 & 0.25 & 0.03\\
3  & 0.59 & 0.37 & 0.04 & 0.34 & 0.51 & 0.15\\
5  & 0.58 & 0.35 & 0.07 & 0.49 & 0.42 & 0.09\\
10 & 0.59 & 0.31 & 0.10 & 0.56 & 0.33 & 0.11\\
\hline
\multicolumn{7}{l}{By number of trials \(n\)}\\
5  & 0.60 & 0.34 & 0.06 & 0.57 & 0.33 & 0.10\\
10 & 0.61 & 0.32 & 0.07 & 0.57 & 0.33 & 0.11\\
20 & 0.62 & 0.31 & 0.06 & 0.53 & 0.38 & 0.09\\
50 & 0.65 & 0.30 & 0.05 & 0.44 & 0.47 & 0.09\\
\hline
\end{tabular}
\caption{Win share marginally by number of categories \(k\) and number of trials \(n\), averaging over the other two design dimensions (\(5{,}000\) symmetric-Dirichlet draws per design cell). Relative to belief concentration (Table~\ref{tab:regime-wins}), the dependence is second-order: the coordinate target is nearly flat in both, and the only visible movements are the binary case \(k=2\) and a mild drift toward squared-distance scoring at large \(n\) for the mean target.}
\label{tab:design-nk}
\end{table}

\paragraph{Robustness.}
Two implementation choices were checked; neither changes the comparison.
First, the linear-functional results are robust to the outcome vector.
The same run also evaluates the extreme-category outcome vector \(x=(0,\ldots,0,1)\) in place of the evenly spaced \(x_i=(i-1)/(k-1)\); the ranking is unchanged, with win shares \(0.56\), \(0.34\), and \(0.10\) for frequency-guessing, squared-distance, and Manhattan scoring, against \(0.53\), \(0.38\), and \(0.10\) for the evenly spaced vector.
Second, optimal-report ties are a measure-zero event under the continuous Dirichlet draws: the final run recorded a tie rate of \(0.0000\) for all three rules, so the lexicographic convention used to select a report when \(R_S(p)\) is not a singleton has no effect on the reported numbers.

\paragraph{Robustness to asymmetric beliefs.}
The main design comparison draws beliefs from symmetric Dirichlet distributions, which are exchangeable across categories.
A symmetric draw cannot produce a systematic asymmetry---a one-dominant, two-mode, graded, or balanced-but-asymmetric prior on the simplex.
Nine asymmetric concentration vectors at \(n=20\), \(k=5\) (\(5{,}000\) draws each, same seed and bounds machinery as the main grid) check whether the regime story extends.
Three are concentrated (at least one \(\alpha_i\le 0.5\)); one is a transition vector with smallest component at \(0.5\); and five are balanced (all \(\alpha_i\ge 2\)), sorted by the max-to-min ratio of the concentration vector (the ``\(\alpha\)-spread'').

\begin{table}[h]
\centering
\small
\setlength{\tabcolsep}{4pt}
\begin{tabular}{lrrrrrr}
\hline
& \multicolumn{3}{c}{Average-coordinate} & \multicolumn{3}{c}{Linear-mean}\\
\cline{2-4}\cline{5-7}
\(\boldsymbol\alpha\) & Guess & Squared & Manh.\ & Guess & Squared & Manh.\\
\hline
\multicolumn{7}{l}{Concentrated-asymmetric (at least one \(\alpha_i\le 0.5\))}\\
\((5, 0.5, 0.5, 0.5, 0.5)\)   & 0.06 & 0.60 & 0.33 & 0.04 & 0.72 & 0.24\\
\((3, 3, 0.3, 0.3, 0.3)\)     & 0.03 & 0.76 & 0.21 & 0.04 & 0.82 & 0.14\\
\((5, 2, 1, 0.5, 0.2)\)       & 0.07 & 0.67 & 0.26 & 0.03 & 0.86 & 0.11\\
\hline
\multicolumn{7}{l}{Transition (smallest \(\alpha_i = 0.5\), no large dominant component)}\\
\((2, 2, 1, 0.5, 0.5)\)       & 0.26 & 0.54 & 0.20 & 0.23 & 0.63 & 0.15\\
\hline
\multicolumn{7}{l}{Balanced-asymmetric (all \(\alpha_i\ge 2\)), ordered by \(\alpha\)-spread \(\max/\min\)}\\
\((3, 3, 3, 2, 2)\)\hspace{3pt}{\footnotesize(1.5)}     & 0.87 & 0.08 & 0.05 & 0.82 & 0.14 & 0.04\\
\((5, 4, 3, 2, 2)\)\hspace{3pt}{\footnotesize(2.5)}     & 0.84 & 0.10 & 0.06 & 0.68 & 0.26 & 0.06\\
\((10, 8, 6, 4, 2)\)\hspace{3pt}{\footnotesize(5.0)}    & 0.76 & 0.17 & 0.07 & 0.52 & 0.41 & 0.07\\
\((15, 10, 5, 2, 2)\)\hspace{3pt}{\footnotesize(7.5)}   & 0.50 & 0.33 & 0.17 & 0.08 & 0.77 & 0.15\\
\((20, 12, 6, 3, 2)\)\hspace{3pt}{\footnotesize(10.0)}  & 0.53 & 0.32 & 0.15 & 0.05 & 0.82 & 0.14\\
\hline
\end{tabular}
\caption{Win share under nine asymmetric concentration vectors at \(n=20\), \(k=5\) (\(5{,}000\) draws each); parentheses give the \(\alpha\)-spread \(\max/\min\) for the balanced cells. Squared-distance scoring dominates the three concentrated-asymmetric cells and the transition cell. Within the balanced regime the average-coordinate ranking remains in favor of frequency-guessing throughout but the margin shrinks with \(\alpha\)-spread; the linear-mean ranking reverses between spread \(5\) and spread \(7.5\), with squared-distance taking over at the steepest spreads.}
\label{tab:regime-wins-asymmetric}
\end{table}

\paragraph{The role of \(\alpha\)-spread within the balanced regime.}
The balanced cells in Table~\ref{tab:regime-wins-asymmetric} are all balanced in the sense that every \(\alpha_i\ge 2\), yet they do not behave identically.
On the average-coordinate target the frequency-guessing dominance holds across all five cells, but the margin contracts monotonically with the \(\alpha\)-spread: from \(79\) points at the flattest vector \((3,3,3,2,2)\) to \(17\) and \(21\) points at the two steepest.
On the linear-mean target the ranking reverses: frequency-guessing wins at spread \(\le 5\) (margins \(11\)--\(68\) points), but squared-distance takes over at spread \(\ge 7.5\) (margins \(62\)--\(68\) points over the runner-up).
A plausible explanation is that the induced beliefs under a wide-spread balanced \(\boldsymbol\alpha\) concentrate tightly around an ordered expected vector, and the mean-target identified set is then sharper under the mean-oriented squared-distance rule than under the mode-oriented frequency-guessing rule.
The refinement does not contradict the headline ``no universal winner'' message, but adds a second dimension to the regime story for asymmetric beliefs: not just concentration versus balance, but, within the balanced regime, how steep the gradient is.
A more thorough mapping of \(\alpha\)-spread effects is left to future work.

Manhattan stays in the \(4\)--\(33\) \% range on both targets across all nine cells, never the outright winner but never far from the leader; its regime-robust character survives intact.
Mean regret tells the same story: the leading rule's regret stays at \(\le 0.003\) in seven of the nine cells, with the largest leader-regret reached at the transition and balanced-graded cells where the rules are closer in win share.
