\documentclass[11pt]{article}

\usepackage[margin=1.15in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}
\usepackage{natbib}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\E}{\mathbb{E}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\1}{\mathbf{1}}
\newcommand{\DeltaK}{\Delta^k}
\newcommand{\OmegaN}{\Omega}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\theoremstyle{plain}

\title{The Informativeness of Frequency-Report Scoring Rules}
\author{Jesper Armouti-Hansen\thanks{University of Bonn.
  Email: \texttt{jesper@armoutihansen.xyz}.}}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
In a multinomial frequency-report environment, a subject has latent beliefs \(p\), but the researcher observes only an incentivized count report \(r\).
We compare frequency-report scoring rules by how sharply that report identifies the latent beliefs.
The inference is recast as a partial-identification problem: each scoring rule maps the report to an identified set of beliefs---those under which the report would have been optimal---from which coordinate and mean bounds follow.
The main analytical result is that squared-distance frequency scoring gives a transparent projection rule, a linear identified set, closed-form coordinate bounds, and linear-program bounds for means.
Frequency-guessing scoring is the known fixed-prize rule with closed-form coordinate and mean bounds; Manhattan distance has an exact identified set, sharp one-dimensional coordinate bounds, and grid-implemented mean bounds.
All three rules share a single structural condition---separability and discrete convexity of an appropriate per-coordinate cost; two further count-loss rules, Hamming and Chebyshev distance, violate it, and Section~\ref{sec:other-rules} takes them up as the boundary of the approach.
No rule is universally most informative. Which one yields the tightest bounds turns on how concentrated the subject's beliefs are: squared-distance scoring when beliefs are concentrated on a few categories, frequency-guessing scoring when they are balanced across them, with a closed-form crossover in the number of positive-report coordinates, which a design comparison then locates as a crossover in the Dirichlet concentration parameter. Manhattan distance is rarely the tightest, but its bounds barely move across regimes, making it the robust choice when the belief regime cannot be anticipated.

\medskip
\noindent\textbf{Keywords:} belief elicitation; scoring rules; frequency reports; partial identification; informativeness; multinomial beliefs.

\smallskip
\noindent\textbf{JEL classification:} C44; C81; C90; D81; D83.
\end{abstract}
\newpage

\input{sections/01_introduction}
\input{sections/02_setup}
\input{sections/03_scoring_rules}
\input{sections/06_design_comparison}
\input{sections/07_discussion}
\newpage

\bibliographystyle{apalike}
\bibliography{references}
\newpage
\input{sections/08_appendix}

\end{document}
